---
title: "CO_businesses"
author: "cyorir"
date: "October 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Colorado information Marketplace offers a large dataset containing geocoded information about Colorado businesses. This dataset is available at:

https://data.colorado.gov/Business/All-CO-businesses-geocoded/k5bm-9tcj

First the dataset must be loaded:

```{r read}
business_data <- read.csv("All_CO_businesses_geocoded.csv")
head(business_data)
```

Each business has a status, which is one of the following:

```{r names}
possible_statuses <- levels(business_data$entitystatus)
possible_statuses
```

For disolved businesses, the date of dissolution is listed in the entityname:

```{r dissolved_name}
suppressMessages(library(dplyr))
dissolved <- business_data %>% filter(as.character(entitystatus) %in% c("Administratively Dissolved",
                                                          "Dissolved (Term Expired)",
                                                          "Judicially Dissolved",
                                                          "Voluntarily Dissolved"))
head(dissolved$entityname)
```

The formation date of dissolved businesses can be plotted over time:

```{r formdate}
suppressMessages(library(lubridate))
dissolved <- dissolved %>% mutate(formdate = mdy(as.character(entityformdate)))
suppressMessages(library(ggplot2))
ggplot(dissolved, aes(x=formdate)) + geom_histogram(bins = 50)
```

Note the peak near the dot-com bubble. The earlier dates are easier to visualize on a log scale:

```{r formdate_log}
ggplot(dissolved, aes(x=formdate)) + geom_histogram(bins = 50) + scale_y_log10()
```

It is more difficult to extract the dissolution year, and many rows will have to be ignored:

```{r dissolved_date}
dissolved <- dissolved %>% mutate(disdate = as.numeric(substr(entityname,nchar(as.character(entityname))-3,nchar(as.character(entityname)))))
summary(dissolved$disdate)
```

Many of the new businesses formed in the dot-com bubble did not last long:

```{r dissolved_plot}
ggplot(dissolved, aes(x=disdate)) + geom_histogram(bins = 28) + xlim(1990,2018)
```

Earlier dates are easier to visualize using a log scale, as previously:

```{r dissolved_plot_log}
ggplot(dissolved, aes(x=disdate)) + geom_histogram(bins = 58) + xlim(1960,2018) + scale_y_log10()
```
